---
title: "DOC data overview"
author: "Eric Oh"
date: "8/13/2019" 
output: github_document
---

This document summarizes key variables from the Philadelphia Department of Corrections (DOC) data. The dataset represents incarcerated person releases from 2007-2016 throughout the Philadelphia area.  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE}
suppressMessages(suppressWarnings(library(ggplot2)))
suppressMessages(suppressWarnings(library(ggthemes)))
suppressMessages(suppressWarnings(library(knitr)))
suppressMessages(suppressWarnings(library(kableExtra)))
suppressMessages(suppressWarnings(library(dplyr)))
suppressMessages(suppressWarnings(library(stringr)))
suppressMessages(suppressWarnings(library(lubridate)))
suppressMessages(suppressWarnings(library(rgdal)))
suppressMessages(suppressWarnings(library(ggmap)))
suppressMessages(suppressWarnings(library(maptools)))
suppressMessages(suppressWarnings(library(cowplot)))
#suppressMessages(suppressWarnings(library(spdep)))

doc_dat <- read.csv("~/Dropbox/doc_project/data/johnson_doc_data/PhilaLegalZip-Table 1.csv")
```

# Zip codes

Let's take a look at from which zip codes the most releases occured.

```{r, echo = FALSE}
zip_code_freq <- data.frame(table(doc_dat$legal_zip_code))
colnames(zip_code_freq) <- c("Zip_code", "Frequency")
zip_code_freq <- zip_code_freq[order(zip_code_freq$Frequency,
                                     decreasing = TRUE),]
zip_code_freq$Percent <- (zip_code_freq$Frequency / sum(zip_code_freq$Frequency)) * 100

#kable(zip_code_freq[1:10,], row.names = FALSE) %>% kable_styling(position = "center")
```

```{r, eval = FALSE, echo = FALSE}
# plot all zip codes with more than 1000 releases
# and group all others in OTHER category

#zip_code_plot_dat <- zip_code_freq[zip_code_freq$Frequency >= 1000,]

#zip_code_others <- data.frame(Zip_code = "Other",
#                              Frequency = sum(zip_code_freq$Frequency[zip_code_freq$Frequency < 1000]),
#                              Percent = 0)

#zip_code_plot_dat <- data.frame(rbind(zip_code_plot_dat, zip_code_others))
```

```{r, fig.align = "center", echo = FALSE}
zip_code_plot_dat <- zip_code_freq[1:10,]
zip_code_plot_dat$Zip_code <- factor(zip_code_plot_dat$Zip_code, 
                                     levels = zip_code_plot_dat$Zip_code[order(-zip_code_plot_dat$Percent)])

ggplot(zip_code_plot_dat, aes(x = Zip_code, y = Frequency)) + 
  geom_bar(stat = "identity", fill = "#599ad3") +
  xlab("Zip code") + ylab("Frequency") + 
  ggtitle("Most frequent zip codes with offenses") + 
  theme_hc()
```

The three zip codes that had the most number of releases is 19124, 19134, and 19140. Let's see if the number of releases has varied much over time. 

```{r, fig.align = "center", echo = FALSE}
top_three_zip <- c(19124, 19134, 19140)
zip_code_trend <- doc_dat[,c("ReleaseYear", "legal_zip_code")]
zip_code_trend <- zip_code_trend[zip_code_trend$legal_zip_code %in% top_three_zip,]

zip_code_trend_count  <- zip_code_trend %>%
  group_by(ReleaseYear, legal_zip_code) %>%
  count(ReleaseYear) %>%
  as.data.frame()

ggplot(zip_code_trend_count,
       aes(x = as.factor(ReleaseYear), y = n, 
           colour = as.factor(legal_zip_code), 
           group = as.factor(legal_zip_code))) +
  geom_line() + 
  geom_point(size = 2.5) + 
  scale_colour_manual(values = c("#00AFBB", "#E7B800", "#FC4E07")) +
  labs(x = "Release year", y = "Number of releases", colour = "Zip codes") + 
  theme_minimal()
```

The number of releases in 19124 seems to have decreased through the years, though not consistently. In 19134, the number of releases has somewhat consistently increased. In 19140, the number of releases rose but went down again. Now we can compare the number of releases across all Philadelphia zip codes.  

```{r, fig.align = "center", echo = FALSE}
philly_zip_shape <- readOGR("~/Dropbox/doc_project/Zipcodes_Poly",
                            "Zipcodes_Poly",
                            stringsAsFactors = FALSE)

philly_zip_code <- read.csv("~/Dropbox/doc_project/Zipcodes_Poly.csv")

philly_zip_shape_df <- fortify(philly_zip_shape, region = "OBJECTID")
philly_zip_shape_df$id <- as.numeric(philly_zip_shape_df$id)

philly_zip_shape_df <- merge(philly_zip_shape_df, 
                             philly_zip_code[,c("OBJECTID", "CODE")],
                             by.x = "id", by.y = "OBJECTID", all.x = TRUE)

doc_dat_philly_map <- doc_dat[doc_dat$legal_zip_code %in% philly_zip_shape_df$CODE,]

offense_by_zip_shape <- doc_dat_philly_map %>%
  group_by(legal_zip_code) %>%
  summarise(count = n())

philly_map_num_offenses_df <- merge(philly_zip_shape_df,
                                    offense_by_zip_shape,
                                    by.x = "CODE", by.y = "legal_zip_code")

ggplot(philly_map_num_offenses_df, 
       aes(x = long, y = lat, 
           group = CODE, fill = count)) + 
  geom_polygon() + 
  coord_equal() + 
  scale_fill_gradientn('Number of releases', colors = topo.colors(3)) + 
  theme(axis.line = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.background = element_blank(),
        panel.border = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.background = element_blank())
```

# Race

Let's take a look at the distribution of different races amongst all offenses.

```{r, fig.align = "center", echo = FALSE}
race_freq <- data.frame(table(doc_dat$race))
colnames(race_freq) <- c("Race", "Frequency")
race_freq <- race_freq[order(race_freq$Frequency,
                             decreasing = TRUE),]
race_freq$Percent <- (race_freq$Frequency / sum(race_freq$Frequency)) * 100

#kable(race_freq, row.names = FALSE) %>% kable_styling(position = "center")

ggplot(race_freq,
       aes(x = as.factor(Race), y = Frequency)) + 
  geom_bar(stat = "identity", fill = "#599ad3") + 
  geom_text(aes(label = Frequency), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5) + 
  labs(x = "Race", y = "Frequency") + 
  theme_minimal()
```


# Sex

Let's take a look at the distribution of sex among all offenses.

```{r, fig.align = "center", echo = FALSE}
sex_freq <- data.frame(table(doc_dat$sex))
colnames(sex_freq) <- c("Sex", "Frequency")
sex_freq <- sex_freq[order(sex_freq$Frequency,
                             decreasing = TRUE),]
sex_freq$Percent <- (sex_freq$Frequency / sum(sex_freq$Frequency)) * 100

#kable(sex_freq, row.names = FALSE) %>% kable_styling(position = "center")

ggplot(sex_freq,
       aes(x = as.factor(Sex), y = Frequency)) + 
  geom_bar(stat = "identity", fill = "#599ad3") + 
  geom_text(aes(label = Frequency), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5) + 
  labs(x = "Sex", y = "Frequency") + 
  theme_minimal()
```


# Offenses

Now let's look at the distribution of offenses among releases persons. Note: there are more unique offense codes than offenses. Not too sure why, need to investigate further. 

```{r, echo = FALSE}
offense_freq <- data.frame(table(doc_dat$offense))
colnames(offense_freq) <- c("Offense", "Frequency")
offense_freq <- offense_freq[order(offense_freq$Frequency,
                             decreasing = TRUE),]
offense_freq$Percent <- (offense_freq$Frequency / sum(offense_freq$Frequency)) * 100

#kable(offense_freq[1:10,], row.names = FALSE) %>% kable_styling(position = "center")
```

Additionally, there seem to be different versions of some offenses (ie. robbery vs. robbery (general)). Not sure what this is. But let's combine them for now. 

```{r, echo = FALSE}
offense_agg <- doc_dat %>%
  mutate(offense = trimws(offense),
         offense = str_replace(offense, " \\(GENERAL\\)", ""))

offense_agg_freq <- data.frame(table(offense_agg$offense))
colnames(offense_agg_freq) <- c("Offense", "Frequency")
offense_agg_freq <- offense_agg_freq[order(offense_agg_freq$Frequency,
                             decreasing = TRUE),]
offense_agg_freq$Percent <- (offense_agg_freq$Frequency / sum(offense_agg_freq$Frequency)) * 100

#kable(offense_agg_freq[1:10,], row.names = FALSE) %>% kable_styling(position = "center")
```

Now let's look at which offenses were most common amongst released persons.

```{r, fig.align = "center", echo = FALSE}
offense_plot_dat <- offense_freq[offense_freq$Frequency >= 1000,]

offense_plot_dat_agg <- do.call(rbind, lapply(c('ROBBERY', 'ASSAULT', 'BURGLARY'),
                                function(x) {
         temp_df <- offense_plot_dat[grep(x, offense_plot_dat$Offense, ignore.case=TRUE),]
         data.frame(Offense = x, 
                    Frequency = sum(temp_df$Frequency), 
                    Percent = sum(temp_df$Percent))}))

offense_plot_dat_agg <- rbind(offense_plot_dat_agg, 
                              offense_plot_dat[c(1, 6, 9, 10),])

offense_plot_dat_agg$Offense <- factor(offense_plot_dat_agg$Offense,
                                       levels = offense_plot_dat_agg$Offense[order(-offense_plot_dat_agg$Percent)])

ggplot(offense_plot_dat_agg, aes(x = Offense, y = Frequency)) + 
  geom_bar(stat = "identity", fill = "#599ad3") +
  scale_x_discrete(labels = c("Drugs", "Robbery", "Assault",
                              "Burglary", "Use\nof Firearm", 
                              "Firearm\nw/o license", "Murder\n(3rd degree)")) + 
  xlab("Offense") + ylab("Frequency") + 
  ggtitle("Most frequent offenses") + 
  theme_hc()
```

From before, we know that 19124, 19132, 19133, 19134, and 19140 had the highest number of releases. What are the top three most common offenses in these five zip codes?

```{r, fig.align = "center", echo = FALSE}
most_common_zip <- c(19124, 19134, 19140,
                     19133, 19132)

# remove white space at the end of the factor 
# level label and remove (GENERAL) 
# to aggregate with non-general ones
offense_by_zip_dat <- doc_dat[doc_dat$legal_zip_code %in% most_common_zip, 
                              c("legal_zip_code", "offense")] %>%
  mutate(offense = trimws(offense),
         offense = str_replace(offense, " \\(GENERAL\\)", ""))

offense_by_zip_dat <- offense_by_zip_dat %>%
  group_by(legal_zip_code, offense) %>%
  summarise(count = n()) %>%
  filter(row_number(desc(count)) < 4) %>%
  as.data.frame()

ggplot(offense_by_zip_dat,
       aes(x = as.factor(legal_zip_code), y = count, 
           fill = offense)) + 
  geom_bar(position = "dodge", stat = "identity") + 
  labs(x = "Zip code", y = "Count of offenses",
       fill = "Offense") + 
  scale_fill_manual(values = c("#00AFBB", "#E7B800", "#FC4E07"),
                    labels = c("Aggravated assault",
                                 "Drug sale",
                                 "Robbery")) + 
  ggtitle("Count of most frequent offenses in the top 5 zip codes") + 
  theme_minimal()

```

In all of the five zip codes, we see that the three most common offenses were drug sales, robbery, and assault. Let's see the distribution of these offenses across all Philadelphia zip codes. 

```{r, fig.align = "center", echo = FALSE}
drug_releases_by_zip_shape <- doc_dat_philly_map[doc_dat_philly_map$offense == offense_freq$Offense[1],]

drug_releases_by_zip_shape <- drug_releases_by_zip_shape %>%
  group_by(legal_zip_code) %>%
  summarise(count = n())

philly_map_drug_releases_df <- merge(philly_zip_shape_df,
                                     drug_releases_by_zip_shape,
                                     by.x = "CODE", by.y = "legal_zip_code",
                                     all.x = TRUE)

philly_map_drug_releases_df$count <- replace(philly_map_drug_releases_df$count,
                                             is.na(philly_map_drug_releases_df$count),
                                             0)

ggplot(philly_map_drug_releases_df, 
       aes(x = long, y = lat, 
           group = CODE, fill = count)) + 
  geom_polygon() + 
  coord_equal() + 
  scale_fill_gradientn('Number of drug\nreleases', 
                       colors = topo.colors(3)) + 
  theme(axis.line = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.background = element_blank(),
        panel.border = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.background = element_blank()) -> philly_map_drug_releases
```


```{r, fig.align = "center", echo = FALSE}

offense_agg_philly_map <- offense_agg[offense_agg$legal_zip_code %in% philly_zip_shape_df$CODE,]
robbery_releases_by_zip_shape <- offense_agg_philly_map[offense_agg_philly_map$offense == offense_agg_freq$Offense[2],]

robbery_releases_by_zip_shape <- robbery_releases_by_zip_shape %>%
  group_by(legal_zip_code) %>%
  summarise(count = n())

philly_map_robbery_releases_df <- merge(philly_zip_shape_df,
                                        robbery_releases_by_zip_shape,
                                        by.x = "CODE", by.y = "legal_zip_code",
                                        all.x = TRUE)

philly_map_robbery_releases_df$count <- replace(philly_map_robbery_releases_df$count,
                                                is.na(philly_map_robbery_releases_df$count),
                                                0)

ggplot(philly_map_robbery_releases_df, 
       aes(x = long, y = lat, 
           group = CODE, fill = count)) + 
  geom_polygon() + 
  coord_equal() + 
  scale_fill_gradientn('Number of robbery\nreleases', 
                       colors = topo.colors(3)) + 
  theme(axis.line = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.background = element_blank(),
        panel.border = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.background = element_blank()) -> philly_map_robbery_releases
```


```{r, fig.align = "center", echo = FALSE}
assault_releases_by_zip_shape <- offense_agg_philly_map[offense_agg_philly_map$offense == offense_agg_freq$Offense[3],]

assault_releases_by_zip_shape <- assault_releases_by_zip_shape %>%
  group_by(legal_zip_code) %>%
  summarise(count = n())

philly_map_assault_releases_df <- merge(philly_zip_shape_df,
                                        assault_releases_by_zip_shape,
                                        by.x = "CODE", by.y = "legal_zip_code",
                                        all.x = TRUE)

philly_map_assault_releases_df$count <- replace(philly_map_assault_releases_df$count,
                                                is.na(philly_map_assault_releases_df$count),
                                                0)

ggplot(philly_map_assault_releases_df, 
       aes(x = long, y = lat, 
           group = CODE, fill = count)) + 
  geom_polygon() + 
  coord_equal() + 
  scale_fill_gradientn('Number of assault\nreleases', 
                       colors = topo.colors(3)) + 
  theme(axis.line = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.background = element_blank(),
        panel.border = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.background = element_blank()) -> philly_map_assault_releases


plot_grid(philly_map_drug_releases,
          philly_map_robbery_releases,
          philly_map_assault_releases,
          nrow = 2, ncol = 2)
```


We can also classify the offenses into violent or non-violent. We consider violent crimes to be robbery, assault, murder, rape, manslaughter, homicide, kidnapping, or any other crimes resulting in bodily injury or death. We plot the number of violent and non-violent offense releases over time. 

```{r, fig.align = "center", echo = FALSE}
violent_keywords <- c("ROBBERY", "ASSAULT", "MURDER",
                      "RAPE", "SEXUAL", "MANSLAUGHTER",
                      "BODILY", "KIDNAPPING", "HOMICIDE",
                      "DEATH")
#not_violent_keyword <- c("VEHICLES")

doc_dat$violent_crime <- as.numeric(str_detect(doc_dat$offense, 
                                               paste(violent_keywords, collapse="|")))

violent_crime_trend <- doc_dat[,c("ReleaseYear", "violent_crime")]

violent_crime_trend_count  <- violent_crime_trend %>%
  group_by(ReleaseYear, violent_crime) %>%
  count(ReleaseYear) %>%
  as.data.frame()

ggplot(violent_crime_trend_count,
       aes(x = as.factor(ReleaseYear), y = n, 
           colour = as.factor(violent_crime), 
           group = as.factor(violent_crime))) +
  geom_line() + 
  geom_point(size = 2.5) + 
  scale_colour_manual(values = c("#00AFBB", "#E7B800"),
                      labels = c("Non-violent", "Violent")) +
  labs(x = "Release year", y = "Number of releases", 
       colour = "Type of crime") + 
  theme_minimal()
```

# Priors

Now let's take a look at the distribution of prior incarcerations for persons released in the data.

```{r, echo = FALSE}
prior_freq <- data.frame(table(doc_dat$Prior.Incs))
colnames(prior_freq) <- c("Prior_incarcerations", "Frequency")
prior_freq <- prior_freq[order(prior_freq$Frequency,
                             decreasing = TRUE),]
prior_freq$Percent <- (prior_freq$Frequency / sum(prior_freq$Frequency)) * 100

#kable(prior_freq, row.names = FALSE) %>% kable_styling(position = "center")
```


```{r, fig.align = "center", echo = FALSE}
prior_plot_dat <- prior_freq[prior_freq$Frequency >= 297,]

prior_others <- data.frame(Prior_incarcerations = ">7",
                           Frequency = sum(prior_freq$Frequency[prior_freq$Frequency < 297]),
                           Percent = 0)

prior_plot_dat <- data.frame(rbind(prior_plot_dat, prior_others))
prior_plot_dat$Prior_incarcerations <- factor(prior_plot_dat$Prior_incarcerations, 
                                     levels = prior_plot_dat$Prior_incarcerations[order(-prior_plot_dat$Percent)])

ggplot(prior_plot_dat, aes(x = Prior_incarcerations, y = Frequency)) + 
  geom_bar(stat = "identity", fill = "#599ad3") +
  xlab("Prior incarcerations") + ylab("Frequency") + 
  ggtitle("Most frequent number of prior incarcerations") + 
  theme_hc()
```


# Sentencing lengths

Let's investigate the lengths of sentenences for all releases and what proportion of the maximum sentence they served. The distributions of the sentence lengths and proportion of maximum sentences served are given below. 

```{r, echo = FALSE}
doc_dat$release_date_format <- parse_date_time(doc_dat$ReleaseDate,
                                               orders = c('d-m-y'))

doc_dat$min_sent_date_format <- parse_date_time(doc_dat$MinDate,
                                                orders = c('d-m-y'))

doc_dat$min_sent_year <- year(doc_dat$min_sent_date_format)

doc_dat$max_sent_date_format <- parse_date_time(doc_dat$MaxDt,
                                                orders = c('d-m-y'))

doc_dat$sentence_length <- time_length(interval(doc_dat$min_sent_date_format,
                                                doc_dat$release_date_format),
                                       "year") + 
  (doc_dat$MinSentYrs + doc_dat$MinSentMos/12)

doc_dat$prop_max_sent_served <- doc_dat$sentence_length / (doc_dat$MaxSentYrs + doc_dat$MaxSentMos/12)

sentence_summary_dat <- data.frame(do.call(rbind, 
                                lapply(doc_dat[, c("min_sent_year",
                                                   "sentence_length",
                                                   "prop_max_sent_served")],
                                       summary)))

#kable(sentence_summary_dat, row.names = FALSE) %>% kable_styling(position = "center")
```

```{r, fig.align = "center", echo = FALSE}
ggplot(doc_dat,
       aes(x = sentence_length)) +
  geom_density(adjust = 2) + 
  labs(x = "Sentence lengths") + 
  ggtitle("Distribution of sentence lengths") +
  theme_minimal()

ggplot(doc_dat,
       aes(x = prop_max_sent_served)) +
  geom_density(adjust = 2) + 
  labs(x = "Proportion of maximum sentence served") + 
  ggtitle("Distribution of proportion of maximum sentence served") +
  theme_minimal()
```


Below are boxplots of sentence lengths in the top five zip codes to see if there are any differences. 

```{r, fig.align = "center", echo = FALSE}
sentence_length_dat <- doc_dat[doc_dat$legal_zip_code %in% most_common_zip,]
sentence_length_by_zip <- sentence_length_dat[,c("legal_zip_code", "sentence_length",
                                                 "prop_max_sent_served")]

sentence_length_by_zip$legal_zip_code <- factor(sentence_length_by_zip$legal_zip_code,
                                                levels = most_common_zip)

ggplot(sentence_length_by_zip,
       aes(x = as.factor(legal_zip_code), y = sentence_length)) +
  geom_boxplot() + 
  labs(x = "Zip code", y = "Sentence length") + 
  ggtitle("Boxplots of sentence length for the top zip codes") + 
  theme_minimal()
  
```


Below are boxplots of proportion of maximum sentence served in the top five zip codes to see if there are any differences. 

```{r, fig.align = "center", echo = FALSE}
ggplot(sentence_length_by_zip,
       aes(x = as.factor(legal_zip_code), y = prop_max_sent_served)) +
  geom_boxplot() + 
  labs(x = "Zip code", y = "Proportion of maximum sentence served") + 
  ggtitle("Boxplots of proportion of max sentence for the top zip codes") + 
  theme_minimal()
```


Now let's compare the sentence lengths and proportion of maximum sentence served across all Philadelphia zip codes. 

```{r, fig.align = "center", echo = FALSE}
doc_dat_philly_map_sentence <- doc_dat[doc_dat$legal_zip_code %in% philly_zip_shape_df$CODE,]
sentence_length_by_zip_shape <- doc_dat_philly_map_sentence[,c("legal_zip_code",
                                                               "sentence_length")]

sentence_length_by_zip_shape <- sentence_length_by_zip_shape %>%
  group_by(legal_zip_code) %>%
  summarise(median_sentence_length = median(sentence_length))

philly_map_sentence_length_df <- merge(philly_zip_shape_df,
                                       sentence_length_by_zip_shape,
                                       by.x = "CODE", by.y = "legal_zip_code",
                                       all.x = TRUE)

ggplot(philly_map_sentence_length_df, 
       aes(x = long, y = lat, 
           group = CODE, fill = median_sentence_length)) + 
  geom_polygon() + 
  coord_equal() + 
  scale_fill_gradientn('Median sentence\nlength', colors = topo.colors(3)) + 
  theme(axis.line = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.background = element_blank(),
        panel.border = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.background = element_blank()) -> philly_map_sentence_length
```


```{r, fig.align = "center", echo = FALSE}
prop_sentence_served_by_zip_shape <- doc_dat_philly_map_sentence[,c("legal_zip_code",
                                                                    "prop_max_sent_served")]

prop_sentence_served_by_zip_shape <- prop_sentence_served_by_zip_shape %>%
  group_by(legal_zip_code) %>%
  summarise(median_sentence_served = median(prop_max_sent_served))

philly_map_prop_sentence_served_df <- merge(philly_zip_shape_df,
                                            prop_sentence_served_by_zip_shape,
                                            by.x = "CODE", by.y = "legal_zip_code",
                                            all.x = TRUE)

ggplot(philly_map_prop_sentence_served_df, 
       aes(x = long, y = lat, 
           group = CODE, fill = median_sentence_served)) + 
  geom_polygon() + 
  coord_equal() + 
  scale_fill_gradientn('Median proportion of\nmaximum sentence served', 
                       colors = topo.colors(3)) + 
  theme(axis.line = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.background = element_blank(),
        panel.border = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.background = element_blank()) -> philly_map_sent_served

plot_grid(philly_map_sentence_length,
          philly_map_sent_served,
          nrow = 1)
```

